\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in,nofoot]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{*1}{*1}

\newcommand{\entry}[4]{
  \noindent\textbf{#1} \hfill #2 \\
  \noindent\textit{#3} \hfill \textit{#4} \\
  \vspace{2pt}
}

\newcommand{\project}[2]{
  \noindent\textbf{#1} \hfill #2 \\
  \vspace{2pt}
}

\begin{document}

\pagenumbering{gobble}

\noindent
\begin{minipage}[t]{0.5\textwidth}
\textbf{\Large GABRIEL SOUZA CASTRO}

\vspace{0.4em}

% \noindent \faMapMarker ~ City, Country ~ \faUser ~ AGE years old \\
% \faIdCard ~ Citizenship
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
\raggedleft
{\color{blue}} \href{https://example.com}{\faPhone \space +55 74 98859 1670} \quad
{\color{blue}} \href{mailto:gabrielcastromail@gmail.com}{\faEnvelope \space gabrielcastromail@gmail.com}

\vspace{0.2em}

{\color{blue}} \href{https://gabrcastro.vercel.app}{\faGlobe \space Website} \quad
{\color{blue}} \href{https://github.com/gabrcastro}{\faGithub \space GitHub} \quad
{\color{blue}} \href{https://linkedin.com/in/gabrielsouzacastro}{\faLinkedin \space LinkedIn} \\
\end{minipage}

\vspace{0.5em}

%LANGUAGES%
\section*{Skills}
\vspace{0.6em}
\item \textbf{Front End:} Nextjs, React, Typescript/Javascript, Angular, HTML, CSS/SCSS, Tailwind CSS, TanStack Query, Zod, Redux, Zustand.
\item \textbf{Technology:} Firebase, Git, RESTful APIs, GitHub, Azure, CI/CD.
\item \textbf{Database:} SQL Server, PostgreSQL, SQLite, MongoDB.
\item \textbf{Back End:} Node.js, Nest.js, C#, .NET.
\item \textbf{Soft Skills:} Communication, Flexibility and Proactivity.
\item \textbf{Languages:} \textbf{Native}: Brazilian Portuguese | \textbf{Intermediate}: English | \textbf{Basic}: Spanish

\vspace{1em}

% Experiences %
\section*{Experience}
\vspace{0.6em}

% Experience 1 %
\entry{Houseasy}{ \space 12/2022 -- 05/2024}
{Front End Developer Pleno}{Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}

\item I developed web applications for the company's internal management using React and Next.js, contributing to a significant increase in sales.
\item I collaborated on the creation of reusable components for the company's website, applying Tailwind CSS to speed up development and ensure visual consistency.
\item I integrated APIs using TanStack Query, which simplified the code and made it easier for new developers to adapt to the project.
\item I optimized website performance, reducing page and image load times by 50\%, which improved user experience and SEO results.
\item I implemented responsive design in the applications, making them more accessible to mobile users and contributing to increased engagement.
\item I managed complex application states with Redux and Context API, providing a more fluid and reliable user experience.

\end{itemize}

% Experience 2 %
\entry{Profile Tecnologia}{ \space 09/2021 -- 09/2022}
{Front End Developer}{Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}

\item I developed a web application for companies, integrating chatbot APIs with Angular and TypeScript to improve customer service.

\item I refactored legacy applications, applying good code practices and updating libraries, which improved the efficiency and organization of the code.

\item I implemented real-time messaging functionalities, integrating the frontend with the backend to improve the user experience.

\item I collaborated on the maintenance of mobile applications using Flutter, expanding the scope of customer service and support.

\end{itemize}

% Experience 3 %
\entry{Quarta Casa}{ \space 08/2021 -- 09/2021}
{Web Developer - Inter}{Remote}
\vspace{-1.6em}
\begin{itemize}
\setlength\itemsep{-0.3em}

\item I developed dashboards and web applications with React.js and TypeScript, contributing to visual analysis and decision-making.

\item I participated in the implementation of RabbitMQ in the backend with Node.js, improving asynchronous communication between services.

\item I carried out research and documentation for the development of dashboards, ensuring continuity and clarity of processes for future implementations.

\end{itemize}



\vspace{1em}
% Projects %
% \section*{Projects}
% \vspace{0.6em}
% \project{Project A | \normalfont{\textit{Technologies}}}{\textbf{Month Year}}
% \vspace{-1.6em}
% \begin{itemize}
% \setlength\itemsep{-0.3em}
% \item Description of project 1.
% \item Description of project 2.
% \item Description of project 3.
% \end{itemize}

% % Educations %
\section*{Education}
\vspace{0.6em}
\entry{UNINTER}{2024 -- in progress}{Bachelor in Computer Engineering}

\vspace{0.5em}

\entry{Faculdade Descomplica}{2022 -- 2023}{Postgraduate Diploma in Data Analysis 
Analysis}

\vspace{0.5em}

\entry{SENAC}{2021 -- 2022}{Postgraduate Diploma in Web Technologies and Innovations}

\vspace{0.5em}

\entry{Faculdade São Salvador}{2017 -- 2020}{Degree in Systems Analysis and Development Technology}

\end{document}
